\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Haiming Liang}}\\
	Guangzhou, China
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  (086) 15626001565 \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ $haiming\_liang@hotmail.com$
\end{center}

\hrule
\vspace{-1em}



\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{South China Normal University}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{M.S. Software Engineering}}
	      {\emph{September 2017 -- July 2019}}
    \item
            \headerrow
	      {\textbf{South China Agricultural University}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{B.S. Software Engineering}}
	      {\emph{September 2008 -- July 2012}}
	      	      
\end{itemize}
\hrule
\vspace{-1em}



\subsection*{\Large Projects}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{Todo List Management System based on Django and React}}

	      {\emph{}}
	      {\emph{Feb 2023 -- Present}}
	      \begin{itemize*}
	      	\item Using Django 4 and rest\_framework, developed backend API with Python programming language, with Model as database interaction module.
	      	\item Using React and react-bootstrap to develop UI to be rendered in Web Browser, implemented CRUD for Todo List.
	      	\item With uwsgi and nginx, this project is deployed on Ali Cloud ECS, the address is http://120.78.90.122:3000/
	      \end{itemize*}

    \item
      \headerrow
      {\textbf{Unified Server Dependencies Management System based on Python}}

      {\emph{}}
      {\emph{July 2022 -- Present}}
      \begin{itemize*}
        \item Built the Server Dependencies Management System with Python 2.7 and BaseHTTPServer, glob, re and ConfigParser are used to handle denpendencies queries from client.
        \item Using urlparse to analyze the query parameters in URL to decide whether to upgrade depencies or not.
        \item This project is developed with Test Driven Developement Methodology, 97 testcases are first developed and then coding is started, ensuring the correctness of 11 endoints. 
      \end{itemize*} 
     \item
      \headerrow
      {\textbf{Instracture Operations Management System based on Node.js}}

      {\emph{}}
      {\emph{July 2022 -- Present}}
      \begin{itemize*}
        \item Using Node.js and MongoDB to develop infrastructure operations management system, using Feathersjs to develop Restful API for the frontend to consume. Support Jenkins Pipeline creation, change request templates management and keystore files management.
        \item This project is deployed with Jenkins Pipeline and Ansible playbook.
        \item This project is developed with Test Driven Developement Methodology with Mocha, Git is used for version control. 
      \end{itemize*} 

       \item
      \headerrow
      {\textbf{Automation Test project for Guangfa Securities Block Chain Certification Resetful API}}

      {\emph{}}
      {\emph{Aug 2021 -- Jun 2022}}
      \begin{itemize*}
        \item Testing Block Chain Certification Restful API with Python, writing testcases with unittest and to fire HTTP requests using requests library. 
        \item Testcases are version controlled in Gitlab and configured to be able to be ran at anytime.
        \item Generate test report based on test result. 
      \end{itemize*}    

      \item
      \headerrow
      {\textbf{Automation Test project for HSBC WPB Process API and System API}}

      {\emph{}}
      {\emph{July 2019 -- July 2021}}
      \begin{itemize*}
        \item Using Java and RestAssurred library to write automation testcases for HSBC WPB Process API and System API. There were various small projects, such as CRUD API and banking trading API. RestAssurred library is used to fire HTTP request and to assert certain response fields are met to requirement.
        \item My role in the team includes running testcases in Jenkins Pipeline and to collect run result for manager approval.
        \item Process API are tested with Behavior Driven Development Testing with Cucumber. 
      \end{itemize*}    
	      	      
	 
   
	      	      
\end{itemize}

\hrule
\vspace{-1em}







\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{InfoSys}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{Node.js developer Python developer}}
	      {\emph{July 2022 -- Present}}
	      \begin{itemize*}
	      	\item Working as a contractor in HSBC infrastructure team, write program to manage keystore file, to create Jenkins pipeline and to interact with third-party services.
	      	\item Maintain server health check shell scripts, create Ansible playbooks to deploy API services.
	      	\item As one of the Agile team, I need to fix API bugs and to analyze server crash, working closely with UI and QA teamates.
                 \item Build an instratructure dependencies management system using Python 2.7, using Test Driven Development to ensure program quality.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{Farben Information Technology}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{Node.js developer Java Web Developer}}
	      {\emph{August 2021 -- July 2022}}
	      \begin{itemize*}
	      	\item Designed and implemented Node.js API for Integrated Authorization Management System in GuangFa Securities, build Docker image and to deploy it to testing environment.
	      	\item Create automation testing script for API, generate test reports.
                \item Design and implement the Block Chain Certificate Restful API project with Test Driven Development in Java programming language. Using SpringBoot to improve development efficiency.
	      \end{itemize*}
    \item   
            \headerrow
            {\textbf{Chinasoft International}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{Java API Automation Tester}}
	      {\emph{July 2019 -- July 2021}}
	      \begin{itemize*}
	      	\item Discuss software requirement inside the Agile team with business analysts, create API test script using Java programming language, to run test cases in Jenkins pipeline.
	      	\item As a QA, I need to collect test reports and hand over to QA lead for review, to make sure software quality according to Jenkins pipeline result.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{Pactera}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{VBA developer}}
	      {\emph{February 2015 -- September 2016}}
	      \begin{itemize*}
	      	\item Develop and maintain Excel VBA scripts for HSBC traders. To analyze business requirement and to perform UAT with end users.
	      \end{itemize*}
    \item
	      \headerrow
	      {\textbf{Bamboo Computer}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{C\# developer}}
	      {\emph{July 2014 -- February 2015}}
	      \begin{itemize*}
	      	\item Maintain a Winform based Jewelry transaction system.
                \item Design and develop an ERP system based on ASP.NET MVC.
	      \end{itemize*}
    \item
	      \headerrow
	      {\textbf{Chengyi Software Development}}
	      {\textbf{Guangzhou, Guangdong}}
	      \headerrow
	      {\emph{Technical Support}}
	      {\emph{June 2012 -- September 2013}}
	      \begin{itemize*}
	      	\item Technical support for Cable network management system.
                \item Production support on Oracle database for customer information.
	      \end{itemize*}     
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Languages:}
	      Node.js, Javascript, Java, Python, SQL, Shell Script
	\item \textbf{Software:}
	      Git/Github, Redis, MongoDB, Atlassian (Jira, Confluence), AWS (DynamoDB, EC2, Lambda), Webstorm, IntelliJ IDEA
\end{itemize}

\hrule
\vspace{-1em}


\end{document}
